Connectome inferences using partial correlation from imaging calcium signal

### 2014-06-13 article.tex
wip experimetns

% Datasets
To assess our method, we have used four datasets provided by the organizer
of the Connectomics challenge : normal-1, normal-2, normal-3, normal-4. Those
datasets are time series of size $n=179500$ of image calcium from simulated
neuronal network \cite{stetter2012model} with $p=1000$ neurons. The networks
to inferred have around 15000 arcs or a density of $0.15\%$ and are similar to those
used to rank challenge participants. Note that our parameter tuning was mainly
done on the \textit{normal-1} dataset and partly on \textit{normal-4} dataset,
therefore it may justify why these networks are better retrieved despite the
fact that some might be simpler to infer.

@@

\begin{table}[H]
\centering
\caption{Inverse correlation (ROC). Improvement of each stage of our approach. Note that we choose the
         \textit{best} threshold (\textcolor{red}{for now 0.11}) for stages 1 to 4.}
\begin{tabular}{*{5}{l}}
\toprule
Stage               & normal-1 & normal-2 & normal-3 & normal-4 \\
\midrule
Nothing             & 0.777 & 0.767 & 0.772 & 0.774 \\
PCA                 & 0.780 & 0.770 & 0.776 & 0.777 \\
Weights             & 0.780 & 0.769 & 0.776 & 0.777 \\
Weights + PCA       & 0.783 & 0.772 & 0.779 & 0.780 \\
H-T                 & 0.893 & 0.891 & 0.891 & 0.886 \\
H-T + PCA           & 0.894 & 0.892 & 0.891 & 0.886 \\
H-T + Weights       & 0.899 & 0.897 & 0.896 & 0.891 \\
H-T + Weights + PCA & 0.900 & 0.898 & 0.896 & 0.892 \\
P-P                 & 0.925 & 0.925 & 0.924 & 0.923 \\
P-P + PCA           & 0.926 & 0.926 & 0.925 & 0.923 \\
P-P + Weights       & 0.931 & 0.930 & 0.928 & 0.927 \\
P-P + Weights + PCA & 0.932 & 0.931 & 0.930 & 0.928 \\
Averaging (PCA)     & 0.943 & 0.942 & 0.942 & 0.939 \\
Stacking            & 0.944 & 0.943 & 0.942 & 0.940 \\
\bottomrule
\end{tabular}
\end{table}

\begin{table}[H]
\centering
\caption{Inverse correlation (P-R). Improvement of each stage of our approach. Note that we choose the
         \textit{best} threshold (\textcolor{red}{for now 0.11}) for stages 1 to 4.}
\begin{tabular}{*{5}{l}}
\toprule
Stage               & normal-1 & normal-2 & normal-3 & normal-4 \\
\midrule
Nothing             & 0.070 & 0.064 & 0.068 & 0.072\\
PCA                 & 0.076 & 0.070 & 0.075 & 0.079\\
Weights             & 0.074 & 0.067 & 0.072 & 0.076\\
Weights + PCA       & 0.080 & 0.073 & 0.079 & 0.083\\
H-T                 & 0.264 & 0.260 & 0.269 & 0.241\\
H-T + PCA           & 0.266 & 0.263 & 0.273 & 0.244\\
H-T + Weights       & 0.280 & 0.273 & 0.281 & 0.251\\
H-T + Weights + PCA & 0.284 & 0.278 & 0.285 & 0.255\\
P-P                 & 0.322 & 0.324 & 0.323 & 0.312\\
P-P + PCA           & 0.347 & 0.352 & 0.355 & 0.341\\
P-P + Weights       & 0.333 & 0.334 & 0.327 & 0.313\\
P-P + Weights + PCA & 0.364 & 0.366 & 0.359 & 0.344\\
Averaging           & 0.403 & 0.404 & 0.398 & 0.388\\
Stacking            & 0.404 & 0.405 & 0.399 & 0.389\\
\bottomrule
\end{tabular}
\end{table}

\begin{table}[H]
\centering
\caption{Correlation (ROC). Improvement of each stage of our approach. Note that we choose the
         \textit{best} threshold (\textcolor{red}{for now 0.11}) for stages 1 to 4.}
\begin{tabular}{*{5}{l}}
\toprule
Stage               & normal-1 & normal-2 & normal-3 & normal-4 \\
\midrule
Nothing             & 0.681 & 0.699 & 0.683 & 0.681\\
Weights             & 0.695 & 0.713 & 0.697 & 0.694\\
H-T                 & 0.876 & 0.873 & 0.877 & 0.869\\
H-T + Weights       & 0.886 & 0.884 & 0.891 & 0.877\\
P-P                 & 0.857 & 0.850 & 0.843 & 0.832\\
P-P + Weights       & 0.826 & 0.823 & 0.817 & 0.799\\
\bottomrule
\end{tabular}
\end{table}

\begin{table}[H]
\centering
\caption{Correlation (P-R). Improvement of each stage of our approach. Note that we choose the
         \textit{best} threshold (\textcolor{red}{for now 0.11}) for stages 1 to 4.}
\begin{tabular}{*{5}{l}}
\toprule
Stage               & normal-1 & normal-2 & normal-3 & normal-4 \\
\midrule
Nothing             & 0.028 & 0.028 & 0.025 & 0.026\\
Weights             & 0.031 & 0.030 & 0.027 & 0.028\\
H-T                 & 0.143 & 0.128 & 0.150 & 0.129\\
H-T + Weights       & 0.153 & 0.145 & 0.170 & 0.132\\
P-P                 & 0.100 & 0.087 & 0.079 & 0.083\\
P-P + Weights       & 0.079 & 0.071 & 0.067 & 0.064\\
\bottomrule
\end{tabular}
\end{table}

>>>>

% Datasets
To assess our method, we have used four datasets provided by the organizer
of the Connectomics challenge : normal-1, normal-2, normal-3, normal-4. Those
datasets are time series of size $T=179500$ of image calcium from simulated
neuronal network \cite{stetter2012model} with $|V|=1000$ neurons. The networks
to inferred have around 15000 edge or a density of $0.15\%$ and are similar to those
used to rank challenge participants. Note that our parameter tuning was mainly
done on the \textit{normal-1} dataset and partly on \textit{normal-4} dataset,
therefore it may justify why these networks are better retrieved despite the
fact that some might be simpler to infer.

@@

\begin{table}[H]
\centering
\caption{Inverse correlation (ROC). Improvement of each stage of our approach. Note that we choose the
         \textit{best} threshold (\textcolor{red}{for now 0.11}) for stages 1 to 4.}
\begin{tabular}{*{5}{l}}
\toprule
Stage               & normal-1 & normal-2 & normal-3 & normal-4 \\
\midrule
Nothing             & 0.777 & 0.767 & 0.772 & 0.774 \\
PCA                 & 0.780 & 0.770 & 0.776 & 0.777 \\
Weights             & 0.780 & 0.769 & 0.776 & 0.777 \\
Weights + PCA       & 0.783 & 0.772 & 0.779 & 0.780 \\
H-T                 & 0.893 & 0.891 & 0.891 & 0.886 \\
H-T + PCA           & 0.894 & 0.892 & 0.891 & 0.886 \\
H-T + Weights       & 0.899 & 0.897 & 0.896 & 0.891 \\
H-T + Weights + PCA & 0.900 & 0.898 & 0.896 & 0.892 \\
P-P                 & 0.925 & 0.925 & 0.924 & 0.923 \\
P-P + PCA           & 0.926 & 0.926 & 0.925 & 0.923 \\
P-P + Weights       & 0.931 & 0.930 & 0.928 & 0.927 \\
P-P + Weights + PCA & 0.932 & 0.931 & 0.930 & 0.928 \\
Averaging           & & & & \\
Stacking            & & & & \\
\bottomrule
\end{tabular}
\end{table}

\begin{table}[H]
\centering
\caption{Inverse correlation (P-R). Improvement of each stage of our approach. Note that we choose the
         \textit{best} threshold (\textcolor{red}{for now 0.11}) for stages 1 to 4.}
\begin{tabular}{*{5}{l}}
\toprule
Stage               & normal-1 & normal-2 & normal-3 & normal-4 \\
\midrule
Nothing             & 0.070 & 0.064 & 0.068 & 0.072\\
PCA                 & 0.076 & 0.070 & 0.075 & 0.079\\
Weights             & 0.074 & 0.067 & 0.072 & 0.076\\
Weights + PCA       & 0.080 & 0.073 & 0.079 & 0.083\\
H-T                 & 0.264 & 0.260 & 0.269 & 0.241\\
H-T + PCA           & 0.266 & 0.263 & 0.273 & 0.244\\
H-T + Weights       & 0.280 & 0.273 & 0.281 & 0.251\\
H-T + Weights + PCA & 0.284 & 0.278 & 0.285 & 0.255\\
P-P                 & 0.322 & 0.324 & 0.323 & 0.312\\
P-P + PCA           & 0.347 & 0.352 & 0.355 & 0.341\\
P-P + Weights       & 0.333 & 0.334 & 0.327 & 0.313\\
P-P + Weights + PCA & 0.364 & 0.366 & 0.359 & 0.344\\
Averaging           & & & & \\
Stacking            & & & & \\
\bottomrule
\end{tabular}
\end{table}

\begin{table}[H]
\centering
\caption{Correlation (ROC). Improvement of each stage of our approach. Note that we choose the
         \textit{best} threshold (\textcolor{red}{for now 0.11}) for stages 1 to 4.}
\begin{tabular}{*{5}{l}}
\toprule
Stage               & normal-1 & normal-2 & normal-3 & normal-4 \\
\midrule
Nothing             & 0.681 & 0.699 & 0.683 & 0.681\\
Weights             & 0.695 & 0.713 & 0.697 & 0.694\\
H-T                 & 0.876 & 0.873 & 0.877 & 0.869\\
H-T + Weights       & 0.886 & 0.884 & 0.891 & 0.877\\
P-P                 & 0.857 & 0.850 & 0.843 & 0.832\\
P-P + Weights       & 0.826 & 0.823 & 0.817 & 0.799\\
Averaging           & & & & \\
Stacking            & & & & \\
\bottomrule
\end{tabular}
\end{table}

\begin{table}[H]
\centering
\caption{Correlation (P-R). Improvement of each stage of our approach. Note that we choose the
         \textit{best} threshold (\textcolor{red}{for now 0.11}) for stages 1 to 4.}
\begin{tabular}{*{5}{l}}
\toprule
Stage               & normal-1 & normal-2 & normal-3 & normal-4 \\
\midrule
Nothing             & 0.028 & 0.028 & 0.025 & 0.026\\
Weights             & 0.031 & 0.030 & 0.027 & 0.028\\
H-T                 & 0.143 & 0.128 & 0.150 & 0.129\\
H-T + Weights       & 0.153 & 0.145 & 0.170 & 0.132\\
P-P                 & 0.100 & 0.087 & 0.079 & 0.083\\
P-P + Weights       & 0.079 & 0.071 & 0.067 & 0.064\\
Averaging           & & & & \\
\bottomrule
\end{tabular}
\end{table}
